### 2023-11-19 paper/project/sample-2col.tex

%% The first command in your LaTeX source must be the \documentclass command.
%%
%% Options:
%% twocolumn : Two column layout.
%% hf: enable header and footer.
\documentclass[
twocolumn,
% hf,
]{ceurart}

%%
%% One can fix some overfulls
\sloppy

%%
%% Minted listings support 
%% Need pygment <http://pygments.org/> <http://pypi.python.org/pypi/Pygments>
\usepackage{listings}
%% auto break lines
\lstset{breaklines=true}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% Rights management information.
%% CC-BY is default license.
\copyrightyear{2022}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

%%
%% This command is for the conference information
\conference{Woodstock'22: Symposium on the irreproducible science,
  June 07--11, 2022, Woodstock, NY}

%%
%% The "title" command
\title{CiteQ: Citation Quality Assessment for Scientific Papers through LLM}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
\author[1]{Yahya Jabary}[%
email=jabaryyahya@gmail.com,
url=https://example.com/,
]
\cormark[1]

\author[1]{Onur Eren Arpacı}[%
orcid=0000-0001-7116-9338,
email=mail@example.com,
url=https://example.com/,
]
\address[1]{University of Waterloo, Ontario, Waterloo, Canada}

\cortext[1]{Corresponding author.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX{} document is presented as an
  article formatted for publication by CEUR-WS in a conference
  proceedings. Based on the ``ceurart'' document class, this article
  presents and explains many of the common variations, as well as many
  of the formatting elements an author may use in the preparation of
  the documentation of their work.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  LaTeX class \sep
  paper template \sep
  paper formatting \sep
  CEUR-WS
\end{keywords}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}

CEUR-WS's article template provides a consistent \LaTeX{} style for
use across CEUR-WS publications, and incorporates accessibility and
metadata-extraction functionality. This document will explain the
major features of the document class.

If you are new to publishing with CEUR-WS, this document is a valuable
guide to the process of preparing your work for publication.

The ``\verb|ceurart|'' document class can be used to prepare articles
for any CEUR-WS publication, and for any stage of publication, from
review to final ``camera-ready'' copy with {\itshape very} few changes
to the source.

This class depends on the following packages
for its proper functioning:

\begin{itemize}
\item \verb|natbib.sty| for citation processing;
\item \verb|geometry.sty| for margin settings;
\item \verb|graphicx.sty| for graphics inclusion;
\item \verb|hyperref.sty| optional package if hyperlinking is required in
  the document;
\item \verb|fontawesome5.sty| optional package for bells and whistles.
\end{itemize}

All the above packages are part of any
standard \LaTeX{} installation.
Therefore, the users need not be
bothered about downloading any extra packages.

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

\section{Template parameters}

There are a number of template
parameters which modify some part of the \verb|ceurart| document class.
This parameters are enclosed in square
brackets and are a part of the \verb|\documentclass| command:
\begin{lstlisting}
  \documentclass[parameter]{ceurart}
\end{lstlisting}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item \verb|twocolumn| : Two column layout.
\item \verb|hf| : Enable header and footer\footnote{You can enable
    the display of page numbers in the final version of the entire
    collection. In this case, you should adhere to the end-to-end
    pagination of individual papers.}.
\end{itemize}

\section{Front matter}

\subsection{Title Information}

The titles of papers should be either all use the emphasizing
capitalized style or they should all use the regular English (or
native language) style. It does not make a good impression if you or
your authors mix the styles.

Use the \verb|\title| command to define the title of your work. Do not
insert line breaks in your title.

\subsection{Title variants}

\verb|\title| command have the below options:
\begin{itemize}
\item \verb|title|: Document title. This is default option. 
\begin{lstlisting}
\title[mode=title]{This is a title}
\end{lstlisting}
You can just omit it, like as follows:
\begin{lstlisting}
\title{This is a title}
\end{lstlisting}

\item \verb|alt|: Alternate title.
\begin{lstlisting}
\title[mode=alt]{This is a alternate title}
\end{lstlisting}

\item \verb|sub|: Sub title.
\begin{lstlisting}
\title[mode=sub]{This is a sub title}
\end{lstlisting}
You can just use \verb|\subtitle| command, as follows:
\begin{lstlisting}
\subtitle{This is a sub title}
\end{lstlisting}

\item \verb|trans|: Translated title.
\begin{lstlisting}
\title[mode=trans]{This is a translated title}
\end{lstlisting}

\item \verb|transsub|: Translated sub title.
\begin{lstlisting}
\title[mode=transsub]{This is a translated sub title}
\end{lstlisting}
\end{itemize}

\subsection{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

\verb|\author| command have the below options:

\begin{itemize}
\item \verb|style| : Style of author name (chinese)
\item \verb|prefix| : Prefix
\item \verb|suffix| : Suffix
\item \verb|degree| : Degree
\item \verb|role| : Role
\item \verb|orcid| : ORCID
\item \verb|email| : E-mail
\item \verb|url| : URL
\end{itemize}

Author names can have some kinds of marks and notes:
\begin{itemize}
\item affiliation mark: \verb|\author[<num>]|.
\end{itemize}

The author names and affiliations could be formatted in two ways:
\begin{enumerate}
\item Group the authors per affiliation.
\item Use an explicit mark to indicate the affiliations.
\end{enumerate}

Author block example:
\begin{lstlisting}
\author[1,2]{Author Name}[%
    prefix=Prof.,
    degree=D.Sc.,
    role=Researcher,
    orcid=0000-0000-000-0000,
    email=name@example.com,
    url=https://name.example.com
]

\address[1]{Affiliation #1}
\address[2]{Affiliation #2}
\end{lstlisting}

\subsection{Abstract and Keywords}

Abstract shall be entered in an environment that starts
with \verb|\begin{abstract}| and ends with
\verb|\end{abstract}|.

\begin{lstlisting}
\begin{abstract}
  This is an abstract.
\end{abstract}
\end{lstlisting}

The key words are enclosed in a \verb|keywords|
environment. Use \verb|\sep| to separate keywords.

\begin{lstlisting}
\begin{keywords}
  First keyword \sep 
  Second keyword \sep 
  Third keyword \sep 
  Fourth keyword
\end{keywords}
\end{lstlisting}

At the end of front matter add \verb|\maketitle| command.

\subsection{Various Marks in the Front Matter}

The front matter becomes complicated due to various kinds
of notes and marks to the title and author names. Marks in
the title will be denoted by a star ($\star$) mark;
footnotes are denoted by super scripted Arabic numerals,
corresponding author by an Conformal asterisk (*) mark.

\subsubsection{Title marks}

Title mark can be entered by the command, \verb|\tnotemark[<num>]|
and the corresponding text can be entered with the command
\verb|\tnotetext[<num>]{<text>}|. An example will be:

\begin{lstlisting}
\title{A better way to format your document for CEUR-WS}

\tnotemark[1]
\tnotetext[1]{You can use this document as the template for preparing your
  publication. We recommend using the latest version of the ceurart style.}
\end{lstlisting}

\verb|\tnotemark| and \verb|\tnotetext| can be anywhere in
the front matter, but should be before \verb|\maketitle| command.

\subsubsection{Author marks}

Author names can have some kinds of marks and notes:
\begin{itemize}
\item footnote mark : \verb|\fnmark[<num>]|
\item footnote text : \verb|\fntext[<num>]{<text>}|
\item corresponding author mark : \verb|\cormark[<num>]|
\item corresponding author text : \verb|\cortext[<num>]{<text>}|
\end{itemize}

\subsubsection{Other marks}

At times, authors want footnotes which leave no marks in
the author names. The note text shall be listed as part of
the front matter notes. Class files provides
\verb|\nonumnote| for this purpose. The usage
\begin{lstlisting}
\nonumnote{<text>}
\end{lstlisting}
and should be entered anywhere before the \verb|\maketitle|
command for this to take effect.

\section{Sectioning Commands}

Your work should use standard \LaTeX{} sectioning commands:
\verb|\section|, \verb|\subsection|,
\verb|\subsubsection|, and
\verb|\paragraph|. They should be numbered; do not remove
the numbering from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is not allowed.

\section{Tables}

The ``\verb|ceurart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed \textit{above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \verb|table| to enclose the table's contents and the
table caption. The contents of the table itself must go in the
\verb|tabular| environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table*}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table*}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \verb|table*| to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table}

\section{Math Equations}

You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}

A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \verb|math| environment,
which can be invoked with the usual
\verb|\begin| \ldots \verb|\end| construction or with
the short form \verb|$| \ldots \verb|$|. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX};
this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty} \frac{1}{n} = 0,
\end{math}
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}

A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \verb|equation|
environment. An unnumbered display equation is produced by the
\verb|displaymath| environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX{}; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty} \frac{1}{n} = 0.
\end{equation}
Notice how it is formatted somewhat differently in
the \verb|displaymath|
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  S_{n} = \sum_{i=1}^{n} x_{i} ,
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \lim_{x \to 0} (1 + x)^{1/x} = e
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader. Figure captions go below the figure. Your figures should
also include a description suitable for screen readers, to
assist the visually-challenged to better understand your work.

Figure captions are placed below the figure.

\section{Citations and Bibliographies}

The use of Bib\TeX{} for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}|
command:
\begin{lstlisting}
\bibliography{bibfile}
\end{lstlisting}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the Bib\TeX{} file.

\subsection{Some examples}

A paginated journal article \cite{Abril07}, an enumerated journal
article \cite{Cohen07}, a reference to an entire issue
\cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
monograph/whole book in a series (see 2a in spec. document)
\cite{Harel79}, a divisible-book such as an anthology or compilation
\cite{Editor00} followed by the same example, however we only output
the series if the volume number is given \cite{Editor00a} (so series
should not be present since it has no vol. no.), a chapter in a
divisible book \cite{Spector90}, a chapter in a divisible book in a
series \cite{Douglass98}, a multi-volume work as book \cite{Knuth97},
an article in a proceedings (of a conference, symposium, workshop for
example) (paginated proceedings article) \cite{Andler79}, a
proceedings article with all possible elements \cite{Smith10}, an
example of an enumerated proceedings article \cite{VanGundy07}, an
informally published work \cite{Harel78}, a doctoral dissertation
\cite{Clarkson85}, a master's thesis: \cite{anisi03}, an online
document / world wide web resource \cite{Thornburg01, Ablamowicz07,
  Poker06}, a video game (Case 1) \cite{Obama08} and (Case 2)
\cite{Novak03} and \cite{Lee05} and (Case 3) a patent
\cite{JoeScientist001}, work accepted for publication \cite{rous08},
prolific author \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other
cites might contain `duplicate' DOI and URLs (some SIAM articles)
\cite{Kirschmer:2010:AEI:1958016.1958018}. Multi-volume works as books
\cite{MR781536} and \cite{MR781537}. A couple of citations with DOIs:
\cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
citations: \cite{TUGInstmem, Thornburg01, R, UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{lstlisting}
\begin{acknowledgments}
  These are different acknowledgments.
\end{acknowledgments}
\end{lstlisting}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered
\verb|\section|; please use the ``\verb|acknowledgments|'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|\appendix|'' command:
\begin{lstlisting}
\appendix
\end{lstlisting}
and note that in the appendix, sections are lettered, not
numbered.

%%
%% The acknowledgments section is defined using the "acknowledgments" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acknowledgments}
  Thanks to the developers of ACM consolidated LaTeX styles
  \url{https://github.com/borisveytsman/acmart} and to the developers
  of Elsevier updated \LaTeX{} templates
  \url{https://www.ctan.org/tex-archive/macros/latex/contrib/els-cas-templates}.  
\end{acknowledgments}

%%
%% Define the bibliography file to be used
\bibliography{sample-ceur}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Online Resources}

The sources for the ceur-art style are available via
\begin{itemize}
\item \href{https://github.com/yamadharma/ceurart}{GitHub},
% \item \href{https://www.overleaf.com/project/5e76702c4acae70001d3bc87}{Overleaf},
\item
  \href{https://www.overleaf.com/latex/templates/template-for-submissions-to-ceur-workshop-proceedings-ceur-ws-dot-org/pkfscdkgkhcq}{Overleaf
    template}.
\end{itemize}

\end{document}

%%
%% End of file

### 2023-11-19 citeq/__main__.py
feat: get references

@@ -12,7 +12,7 @@ from db import Researcher, Paper, Authorship, Citation, engine
 from sqlalchemy.orm import Session
 from types import SimpleNamespace
 import backoff
-
+from dotenv import load_dotenv
 
 from logger import LOG_SINGLETON as LOG, trace
 
@@ -51,8 +51,8 @@ def is_cached_get_path(cache_key: str, filename: str) -> Tuple[bool, str]:
 
 
 @backoff.on_exception(backoff.expo, requests.exceptions.RequestException, max_tries=8)
-def get_url(url):
-    r = requests.get(url)
+def get_url(url, headers=None):
+    r = requests.get(url, headers=headers)
 
     if r.status_code != 200:
         LOG.warning(f"request failed with status code {r.status_code} - retrying")
@@ -317,9 +317,10 @@ class SemanticScholarClient:
         return papers
 
     @staticmethod
-    def get_citations(db, ss_researcher_obj: dict) -> list:
+    def get_citations(db, ss_researcher_obj: dict):
         # fetch papers
         papers = db.session.query(Paper).filter(Paper.citations_added == False).all()
+        headers = {"x-api-key": os.getenv("S2_API_KEY")} if os.getenv("S2_API_KEY") else None
 
         LOG.info(f"fetching citations")
         # fetch citations of papers
@@ -328,18 +329,16 @@ class SemanticScholarClient:
         for paper in papers:
             citations = []
             id = paper.semantic_scholar_id
-            paper_query = f"https://api.semanticscholar.org/graph/v1/paper/{id}/citations?limit=1000&fields=contexts,intents,paperId"
+            paper_query = f"https://api.semanticscholar.org/graph/v1/paper/{id}/citations?fields=contexts,intents,paperId"
 
             # paginate through citations (also avoid rate limit)
-            offset = None
-            while (offset is None) or (offset != 0):
-                ppquery = paper_query + ("" if offset is None else f"&offset={offset}")
-                response = get_url(ppquery).json()
+            offset: None | int = 0
+            while offset is not None:
+                ppquery = paper_query + ("" if offset == 0 else f"&offset={offset}")
+                response = get_url(ppquery, headers=headers).json()
                 assert response
                 citations.extend(response["data"])
-                offset = response["offset"]
-                LOG.info(f"\tprogress: {c}/{len(papers)}")
-                c += 1
+                offset = response.get("next")
 
             # add citations to db
             for citation in citations:
[…]

### 2023-12-21 paper/main.tex
update

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{acmart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{acmart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf]{acmart}

\usepackage{bm}
\usepackage{algorithm}
\usepackage[noEnd=True]{algpseudocodex}
\usepackage{tikz}
\usepackage{listings}
\usepackage{float}
\floatstyle{plain}
\newfloat{Figure}{t}{myc}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{verylightgray}{rgb}{.97,.97,.97}

\lstset{frame=tb,
  language=Python,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  backgroundcolor = \color{verylightgray},
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{black},
  stringstyle=\color{black},
  breaklines=true,
  breakautoindent=false,
  breakindent=0pt,
  breakatwhitespace=true,
  tabsize=3
}

\usepackage{pgfplots}
\pgfplotsset{
    width=8cm,
    compat=1.9,
    legend style={
      fill,
      at={(0.50,-0.35)},
      legend columns=1,
      legend cell align=left,
      anchor=north
      }
    }
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmlicensed}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation emai}{June 03--05,
  2018}{Woodstock, NY}
%%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%%  June 03--05, 2018, Woodstock, NY}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{CiteQ: Analysis on Citation Purposes: University of Waterloo Computer Science Faculty Case Study}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Onur Eren Arpaci}
\email{oearpaci@uwaterloo.ca}
\affiliation{%
  \institution{University of Waterloo}
  \streetaddress{200 University Ave W}
  \city{Waterloo}
  \state{Ontario}
  \country{Canada}
  \postcode{N2L 3G1}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Arpaci}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  TODO: Write abstract
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
    <ccs2012>
       <concept>
           <concept_id>10002951.10003317</concept_id>
           <concept_desc>Information systems~Information retrieval</concept_desc>
           <concept_significance>300</concept_significance>
           </concept>
       <concept>
           <concept_id>10002944.10011123.10011131</concept_id>
           <concept_desc>General and reference~Experimentation</concept_desc>
           <concept_significance>500</concept_significance>
           </concept>
       <concept>
           <concept_id>10003456.10010927.10003619</concept_id>
           <concept_desc>Social and professional topics~Cultural characteristics</concept_desc>
           <concept_significance>100</concept_significance>
           </concept>
     </ccs2012>
\end{CCSXML}

\ccsdesc[300]{Information systems~Information retrieval}
\ccsdesc[500]{General and reference~Experimentation}
\ccsdesc[100]{Social and professional topics~Cultural characteristics}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Citation Purpose, Citation Analysis, Citation Trends, LLM classification}
%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.

\received{20 February 2007}
\received[revised]{12 March 2009}
\received[accepted]{5 June 2009}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
The predominant and widely recognized scientometric indicator is the number 
of citations a paper garners. Nevertheless, it's crucial to acknowledge that 
papers can be cited for diverse reasons. A citation may stem from a paper 
serving as the foundational work for current research, acting as a competitor 
in the field, or being subject to critique.

The purpose of this paper is to study the citation purposes and its affects
on other scientometric indicators. We aim to answer the following research 
questions:

\begin{enumerate}
    \item[RQ1] Do the citation purposes affect the total number of
    citations a paper or a researcher receives? (i.e. is there a karma effect?)
    \item[RQ2] How does the distribution of citation purposes change over time?
    \item[RQ3] Is there any difference in the distribution of citation purposes
    between same institution researchers and different institution researchers? 
    \item[RQ4] How does the distribution of citation purposes change over the
    duration of a researcher's career?
\end{enumerate}

To answer these questions, we collected the publication and citation data of
the University of Waterloo Computer Science faculty members. We then used
the large language model (LLM) llama2 \cite{touvron2023llama} to classify the citation 
purposes of each paper. We then analyzed this data to answer the research questions.

\section{Related Work}
Our work is related to a large body of research on citation analysis. Abu-Jbara et. al. \cite{abu2013purpose} provides a good starting point for citation purpose analysis. They propose 6 classes of citation purposes: criticizing, comparison, use, substantiating, basis, and neutral. We use these classes as the basis for our analysis.

\section{Methodology}
\subsection{Data Collection}
We used the Semantic Scholar (SS) API to collect the publication and citation data of all current (as of this writing) members of the University of Waterloo Computer Science faculty members. SS provides an API endpoint to retrieve the context of a citation. We used this endpoint to retrieve the citation context of each citation
made by a faculty member or to a faculty member. In total we collected data about 96 faculty members, 9,438 papers, and 697,609 citations. We formed an SQLite database, with the scheme shown in Figure \ref{fig:citeq-scheme}, to facilitate flexible querying of the data.

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{citeq-scheme.png}
    \caption{CiteQ database scheme}
    \label{fig:citeq-scheme}
\end{figure}

\subsection{Citation Purpose Classification}
We experimented with a number of LLMs including chatGPT-3.5 \cite{brown2020language}, chatGPT-4.5 \cite{openai2023gpt4}, mistral \cite{jiang2023mistral}, and llama2 \cite{touvron2023llama}. Although chatGPT models performed slightly better in terms of accuracy, we decided to use llama2 with 7 billion parameters due to its low cost. We used 5 RTX4090 GPUs for 10 hours to classify the citation purposes of all 697,609 citations.

We used the following citation purpose classes: criticizing, comparison, use, substantiating, basis, and neutral. The Figure \ref{figure:prompt-template} shows the prompt template we used.

\subsubsection{Evaluation}
We hand labeled 100 citations to evaluate the accuracy of the classification.
The results are shown in Table \ref{table:evaluation}. We achieved an accuracy of 0.82. The accuracy of the classification is not as high as we would like. However, we believe that it is sufficient for our purposes.

\begin{table}[h]
    \centering
    \begin{tabular}{|l|l|l|l|l|}
        \hline
        \textbf{Class/Model} & \textbf{llama2} & \textbf{mistral} & \textbf{GPT-3.5} & \textbf{GPT-4.5} \\ \hline
        Criticizing & 0.75 & 0.75 & 0.75 & 0.75 \\ \hline
        Comparison & 0.75 & 0.75 & 0.75 & 0.75 \\ \hline
        Use & 0.75 & 0.75 & 0.75 & 0.75 \\ \hline
        Substantiating & 0.75 & 0.75 & 0.75 & 0.75 \\ \hline
        Basis & 0.75 & 0.75 & 0.75 & 0.75 \\ \hline
        Neutral & 0.75 & 0.75 & 0.75 & 0.75 \\ \hline
        \textbf{Average} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} \\ \hline
    \end{tabular}
    \caption{Precision of different LLMs in citation purpose classification}
    \label{table:evaluation}
\end{table}

\begin{figure}
\begin{lstlisting}
"""
The following is a set of citation purpose categories, each category name is followed by a description of the category and an example of a sentence that belongs to this category.

Name: Criticizing
Description: Criticism can be positive or negative. A citing sentence is classified as "criticizing" when it mentions the weakness/strengths of the cited approach, negatively/positively criticizes the cited approach, negatively/positively evaluates the cited source.
Example: Chiang (2005) introduced a constituent feature to reward phrases that match a syntactic tree but did not yield significant improvement.

Name: Comparison
Description: A citing sentence is classified as "comparison" when it compares or contrasts the work in the cited paper to the author's work. It overlaps with the first category when the citing sentence says one approach is not as good as the other approach. In this case we use the first category.
Example: Our approach permits an alternative to minimum error-rate training (MERT; Och, 2003);

Name: Use
Description: A citing sentence is classified as "use" when the citing paper uses the method, idea or tool of the cited paper.
Example: We perform the MERT training (Och, 2003) to tune the optimal feature weights on the development set.

Name: Substantiating
Description: A citing sentence is classified as "substantiating" when the results, claims of the citing work substantiate, verify the cited paper and support each other.
Example: It was found to produce automated scores, which strongly correlate with human judgements about translation fluency (Papineni et al. , 2002).

Name: Basis
Description: A citing sentence is classified as "basis" when the author uses the cited work as starting point or motivation and extends on the cited work.
Example: Our model is derived from the hidden-markov model for word alignment (Vogel et al., 1996; Och and Ney, 2000).

Name: Neutral (Other)
Description: A citing sentence is classified as "neutral" when it is a neutral description of the cited work or if it doesn't come under any of the above categories.
Example: The solutions of these problems depend heavily on the quality of the word alignment (Och and Ney, 2000).

Classify the following in text citation into one of these categories. Only use a single category for each citation. Respond with only a single word, the name of the category.

{Citation Context}
"""
\end{lstlisting}
\caption{Prompt template used for citation purpose classification}
\label{figure:prompt-template}
\end{figure}

\section{Results}
Initial results

\begin{Figure}
  \begin{tikzpicture}
  \begin{axis}[
      symbolic x 
      coords={criticizing, comparison, use, substantiating, basis, neutral},
      scaled ticks=false,
      style={/pgf/number format/1000 sep=},
      xtick=data,
      xticklabel style = {rotate=30,anchor=east},
      ytick distance=50000,
      ylabel=Number of Vulnerabilities,
      point meta={(y/697609)*100},
      nodes near coords={\pgfmathprintnumber\pgfplotspointmeta\%}]
      \addplot[ybar,fill=gray] coordinates {
          (criticizing, 560986)
          (comparison, 12122)
          (use,43646)
          (substantiating, 14860)
          (basis, 8057)
          (neutral, 57938)
      };
  \end{axis}
  \end{tikzpicture}
  \caption{Distribution of Vulnerabilities }
  \label{graph:1}
  \end{Figure}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
% \begin{acks}
% To Robert, for the bagels and explaining CMYK and color spaces.
% \end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

### 2023-12-21 citeq/__main__.py

@@ -426,8 +426,8 @@ class OllamaSentimentClassifier:
             for i in range(start, end, batch_size):
                 citations = db.session.query(Citation).offset(i).limit(batch_size).all()
                 for citation in citations:
-                    if citation.llm_purpose is not None:
-                        continue
+                    # if citation.llm_purpose is not None:
+                    #     continue
                     llm_purpose = LlmClassifier.get_sentiment_class(citation.context)
                     if to_csv:
                         with open("llm_purpose.csv", "a") as f:

### 2023-12-21 citeq/evaluate.py

@@ -1,0 +1,55 @@
+from db import Researcher, Paper, Authorship, Citation, engine
+from sqlalchemy.orm import Session
+from sqlalchemy.sql.functions import random
+from tqdm import tqdm
+
+from llm_classifier import LlmClassifier, SentimentClass
+
+# load environment variables
+import os
+from dotenv import load_dotenv
+
+load_dotenv()
+
+# Create a session to use the tables
+session = Session(engine)
+
+# Read the already annotated citations
+annotated_citations = []
+with open("citations_annotated.csv", "r") as f:
+    citations = f.readlines()
+    for citation in citations:
+        annotated_citations.append(citation.strip().split(","))
+
+# get the llm annotations
+llm_annotations = []
+for citation in tqdm(annotated_citations):
+    citation_context = session.query(Citation).filter(Citation.id == citation[0]).first().context
+    predicted_class = LlmClassifier.get_sentiment_class(citation_context, "mistral")
+    llm_annotations.append([citation[0], int(citation[1] if citation[1] != 3 else "2"), predicted_class.value])
+
+# write the llm annotations to a file
+with open("llm_annotations_mistral_inst.csv", "w") as f:
+    for annotation in llm_annotations:
+        f.write(f"{annotation[0]},{annotation[1]},{annotation[2]}\n")
+
+# calculate precision, and recall for each class
+tp = [0, 0, 0, 0]
+fp = [0, 0, 0, 0]
+fn = [0, 0, 0, 0]
+
+for annotation in llm_annotations:
+    if annotation[1] == annotation[2]:
+        tp[annotation[1]] += 1
+    else:
+        fp[annotation[2]] += 1
+        fn[annotation[1]] += 1
+
+precision = [0, 0, 0, 0]
+recall = [0, 0, 0, 0]
+for i in range(4):
+    precision[i] = tp[i] / (tp[i] + fp[i]) if tp[i] + fp[i] != 0 else 0
+    recall[i] = tp[i] / (tp[i] + fn[i])
+
+print(f"Precision: {precision}")
+print(f"Recall: {recall}")

### 2023-12-21 citeq/insert_llm_out.py

@@ -1,0 +1,30 @@
+from db import Researcher, Paper, Authorship, Citation, engine
+from sqlalchemy.orm import Session
+from sqlalchemy.sql.functions import random
+from enum import Enum
+from tqdm import tqdm
+
+
+class SentimentClass(Enum):
+    CRITICIZING = 0
+    COMPARISON = 1
+    USE = 2
+    SUBSTANTIATING = 3
+    BASIS = 4
+    NEUTRAL_OR_UNKNOWN = 5
+
+
+# Create a session to use the tables
+session = Session(engine)
+
+# Update the citation purposes with the llm output
+with open("llm_purpose_5.csv", "r") as f:
+    citations = f.readlines()
+    for citation in tqdm(citations):
+        c_id, annotation = citation.split(",")
+        c_id = int(c_id)
+        citation = session.query(Citation).filter(Citation.id == c_id).first()
+        citation.llm_purpose = annotation.strip()
+        session.commit()
+
+    session.close()

### 2023-12-21 citeq/llm_classifier.py

@@ -5,67 +5,200 @@ from logger import LOG_SINGLETON as LOG, trace
 from thefuzz import fuzz
 from langchain.llms import Ollama
 
+from langchain_community.chat_models import ChatOpenAI
+from langchain.schema import HumanMessage, SystemMessage
+import backoff
+import random
+
+import os
+
+os.environ["OPENAI_API_KEY"] = ""
 
 PROMPT = """
 The following is a set of citation purpose categories, each category name is followed by a description of the category and an example of a sentence that belongs to this category.
 
 Name: Criticizing
-Description: Criticism can be positive or negative. A citing sentence is classified as “criticizing” when it mentions the weakness/strengths of the cited approach, negatively/positively criticizes the cited approach, negatively/positively evaluates the cited source.
+Description: A citing sentence is classified as "criticizing" when it mentions the weakness of the cited approach, negatively criticizes the cited approach, negatively evaluates the cited source.
 Example: Chiang (2005) introduced a constituent feature to reward phrases that match a syntactic tree but did not yield significant improvement.
 
 Name: Comparison
-Description: A citing sentence is classified as "comparison” when it compares or contrasts the work in the cited paper to the author’s work. It overlaps with the first category when the citing sentence says one approach is not as good as the other approach. In this case we use the first category.
+Description: A citing sentence is classified as "comparison" when it compares or contrasts the work in the cited paper to the author's work. It overlaps with the first category when the citing sentence says one approach is not as good as the other approach. In this case we use the first category.
 Example: Our approach permits an alternative to minimum error-rate training (MERT; Och, 2003);
 
 Name: Use
-Description: A citing sentence is classified as "use” when the citing paper uses the method, idea or tool of the cited paper.
+Description: A citing sentence is classified as "use" when the citing paper uses the method, idea or tool of the cited paper.
 Example: We perform the MERT training (Och, 2003) to tune the optimal feature weights on the development set.
 
 Name: Substantiating
-Description: A citing sentence is classified as “substantiating” when the results, claims of the citing work substantiate, verify the cited paper and support each other.
+Description: A citing sentence is classified as "substantiating" when the results, claims of the citing work substantiate, verify the cited paper and support each other.
 Example: It was found to produce automated scores, which strongly correlate with human judgements about translation fluency (Papineni et al. , 2002).
 
 Name: Basis
[…]

### 2023-12-21 setup.sh

@@ -1,0 +1,25 @@
+cd ~
+git clone https://github.com/sueszli/citeQ.git
+cd citeQ/
+git checkout experinment
+sudo apt-get install -y pciutils
+curl https://ollama.ai/install.sh | sh
+
+#open terminal serve ollama
+ollama serve
+
+#back to first terminal
+ollama pull llama2
+pip install gdown
+gdown 1xYasfiWA3aeXT-pb-MlFLEpbnEyM9lbq
+mv citeQ_waterloo_profs.db citeQ.db
+
+pip install thefuzz
+pip install PyPDF2
+pip install sqlalchemy
+pip install backoff
+pip install python-dotenv
+pip install rich
+pip install langchain
+
+python citeq -c --start 559000 --end 697609

### 2023-12-30 paper/main.tex
paper content done

@@
 \usepackage{float}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{graphicx}
+\usepackage{xcolor}
+\usepackage{multirow,siunitx}
 \floatstyle{plain}
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{CiteQ: Analysis on Citation Purposes: University of Waterloo Computer Science Faculty Case Study}
+\title{CiteQ: Analysis on Citation Sentiment: University of Waterloo Computer Science Faculty Case Study}
 
@@
 \begin{abstract}
-  TODO: Write abstract
+While citation count and H-index is the most important metrics for measuring impact in Science, the intention of the given citation is usually overlooked.
+To examine the affects of citation sentiments on academic success, this paper conducts a large scale empirical study on University of Waterloo Computer Science faculty members' publication data.
+We show a negative correlation between H-index and the percentage of negative citations given by that researcher.
+We also show a positive correlation between number of papers published by a researcher and percentage of neutral citations given by that researcher.
+In addition we discuss the changes in the distribution of citation sentiments over time and the differences between same institution and different institution citation sentiments.
+We also provide a dataset of 9,438 papers' metadata and 697,609 citations with their citation sentiments for future research.
 \end{abstract}
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{Citation Purpose, Citation Analysis, Citation Trends, LLM classification}
+\keywords{Citation Sentiment, Citation Analysis, Citation Trends, LLM classification}
 %% A "teaser" image appears between the author and affiliation
@@
 
-The purpose of this paper is to study the citation purposes and its affects
-on other scientometric indicators. We aim to answer the following research 
+The purpose of this paper is to study the citation sentiments and its affects
+on citation counts. We aim to answer the following research 
 questions:
@@
 \begin{enumerate}
-    \item[RQ1] Do the citation purposes affect the total number of
+    \item[RQ1] Do the citation sentiments affect the total number of
     citations a paper or a researcher receives? (i.e. is there a karma effect?)
-    \item[RQ2] How does the distribution of citation purposes change over time?
-    \item[RQ3] Is there any difference in the distribution of citation purposes
+    \item[RQ2] How does the distribution of citation sentiments change over the
+    duration of a researcher's career?
+    \item[RQ3] How did the distribution of citation sentiments change over time?
+    \item[RQ4] Is there any difference in the distribution of citation sentiments
     between same institution researchers and different institution researchers? 
-    \item[RQ4] How does the distribution of citation purposes change over the
-    duration of a researcher's career?
 \end{enumerate}
 
-To answer these questions, we collected the publication and citation data of
+We collected the publication and citation data of
 the University of Waterloo Computer Science faculty members. We then used
-the large language model (LLM) llama2 \cite{touvron2023llama} to classify the citation 
-purposes of each paper. We then analyzed this data to answer the research questions.
+the large language model (LLM) Solar 10.7B \cite{upstage2023solar} to classify the citation 
+sentiments of each paper. We then analyzed this data to answer the research questions.
 
 \section{Related Work}
-Our work is related to a large body of research on citation analysis.
-Abu-Jbara et.
-al.
-\cite{abu2013purpose} provides a good starting point for citation purpose analysis.
-They propose 6 classes of citation purposes: criticizing, comparison, use, substantiating, basis, and neutral.
-We use these classes as the basis for our analysis.
+There is a large body of research on citation analysis.
+Most of these studies use the ACL Anthology \cite{bird2008acl} as their dataset.
+ACL Anthology is a dataset of NLP papers and their citations.
+Using the ACL Anthology creates two main differences from our study.
+First, it provides more contextual metadata about the citations than our dataset, such as the position of the citation in the paper, the section of the paper that the citation is in, etc.
+Second, it provides a large enough training dataset to train or finetune any kind of model, which our dataset also lacks.
+\cite{athar2011sentiment, athar2012context, abu2013purpose, hernandez2015citation} are some of the studies that use the ACL Anthology dataset.
+They are generally focusing on the task of citation sentiment classification itself and they do not analyze the output of this classification.
+None of the studies we have found use LLMs for classification.
+Most use sentence or word embeddings.
+
+\cite{yan2020relationship}, \cite{yan2020authors} are some of the studies that analyze the citation sentiment classification output.
+\cite{yan2020relationship} analyze the relationship between journal impact and the citation sentiment.
+They use PubMed Central dataset \cite{pubmed} for this study.
+\cite{yan2020authors} analyze the relationship between Nobel prize winners and their citation sentiments pre and post Nobel prize.
+They manually gather a 100 paper dataset for this study.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{citeq-scheme.png}
+  \caption{CiteQ database scheme}
+  \label{fig:citeq-scheme}
+\end{figure}
+
+\sisetup{table-format=2.2} 
+\begin{table*}
+\centering
+    \begin{tabular}{|l|S|S|S|S|S|S|S|S|S|S|}           \hline 
+\multirow{2}{*}{type}    & \multicolumn{2}{c|}{Positive}    &\multicolumn{2}{c|}{Negative}  &\multicolumn{2}{c|}{Neutral}  &\multicolumn{2}{c|}{Bad Context} &\multicolumn{2}{c|}{\textbf{Average}}  \\   \cline{2-11}
+  &{Prec.} & {Rec.} & {Prec.}  & {Rec.} &{Prec.}  & {Rec.} &{Prec.} &{Rec.}  &{Prec.}  & {Rec.}         \\   \hline 
+Solar 10.7B& 0.68 &0.41 & 0.67 & \textbf{0.67} & \textbf{0.47} & 0.87 & 0.90 & 0.44 &0.68 & \textbf{0.60} \\ \hline  
+GPT-4.5 & \textbf{0.87} & 0.19 & 0.71 & 0.62 & 0.43 & \textbf{0.96} & 0.92 & \textbf{0.52} & \textbf{0.73} & 0.57 \\ \hline
+GPT-3.5 & 0.50 & \textbf{0.95} & \textbf{0.80} & 0.50 & 0.36 & 0.21 & \textbf{1.00} & 0.26 & 0.66 & 0.47\\   \hline
+mistral 7x8B & 0.70 & 0.38 & 0.71 & 0.56 & 0.41 & 0.84 & 0.60 & 0.26 & 0.60 & 0.51\\ \hline
+llama2 7B & 0.39 & 0.75 & 0.60 & 0.375 & 0.34 & 0.25 & \textbf{1.00} & 0.04 & 0.58 & 0.35\\   \hline 
+mistral & 0.48 & 0.27 & 0.36 & 0.50 & 0.43 & 0.87 & 0.75 & 0.13 & 0.50 & 0.44\\ \hline
+ \end{tabular}
+\caption{Evaluation results of the LLMs}
+\label{table:evaluation}
+\end{table*}
 
@@
 We formed an SQLite database, with the scheme shown in Figure \ref{fig:citeq-scheme}, to facilitate flexible querying of the data.
+This database is publicly available at \url{https://github.com/onurerenarpaci/citeQ.git}.
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\linewidth]{citeq-scheme.png}
-    \caption{CiteQ database scheme}
-    \label{fig:citeq-scheme}
-\end{figure}
+\subsection{Citation Sentiment Classification}
+We experimented with a number of LLMs including chatGPT-3.5 \cite{brown2020language}, chatGPT-4.5 \cite{openai2023gpt4}, mistral and mistral 7x8B \cite{jiang2023mistral}, llama2 \cite{touvron2023llama} and Solar 10.7B \cite{upstage2023solar}.
+Among these, only promising results were obtained from Solar 10.7B and \cite{openai2023gpt4}.
+Since with the size of the dataset we had, we could not afford to run the classification on GPT-4.5, so we chose Solar 10.7B as our LLM.
 
-\subsection{Citation Purpose Classification}
-We experimented with a number of LLMs including chatGPT-3.5 \cite{brown2020language}, chatGPT-4.5 \cite{openai2023gpt4}, mistral \cite{jiang2023mistral}, and llama2 \cite{touvron2023llama}.
-Although chatGPT models performed slightly better in terms of accuracy, we decided to use llama2 with 7 billion parameters due to its low cost.
-We used 5 RTX4090 GPUs for 10 hours to classify the citation purposes of all 697,609 citations.
+We used the following citation purpose classes: positive, neutral, negative, bad context.
+The positive class includes citations that are talking about the strengths of the paper, important it is.
+The negative class includes citations that are talking about the weaknesses of the paper, or talks about their solution being better than the paper's solution.
+The neutral class includes citations that are talking about the paper without any positive or negative sentiment.
+The bad context class is for badly captured citation contexts that do not contain any information about the citation sentiment.
+With the satisfactory precision on the bad context class, we removed all the citations labeled as bad context from our dataset for all the analysis we have conducted.
+You can see the prompt template we used in Appendix \ref{appendix:classification-prompt}.
 
-We used the following citation purpose classes: criticizing, comparison, use, substantiating, basis, and neutral. The Figure \ref{figure:prompt-template} shows the prompt template we used.
+We used 6 Nvidia A100 80GB GPUs to run the classification. The total inference time was 1 day and 4 hours.
 
@@
 The results are shown in Table \ref{table:evaluation}.
-We achieved an accuracy of 0.82.
-The accuracy of the classification is not as high as we would like.
-However, we believe that it is sufficient for our purposes.
-
-\begin{table}[h]
-    \centering
-    \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Class/Model} & \textbf{llama2} & \textbf{mistral} & \textbf{GPT-3.5} & \textbf{GPT-4.5} \\ \hline
-        Criticizing & 0.75 & 0.75 & 0.75 & 0.75 \\ \hline
-        Comparison & 0.75 & 0.75 & 0.75 & 0.75 \\ \hline
-        Use & 0.75 & 0.75 & 0.75 & 0.75 \\ \hline
-        Substantiating & 0.75 & 0.75 & 0.75 & 0.75 \\ \hline
-        Basis & 0.75 & 0.75 & 0.75 & 0.75 \\ \hline
-        Neutral & 0.75 & 0.75 & 0.75 & 0.75 \\ \hline
-        \textbf{Average} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} \\ \hline
-    \end{tabular}
-    \caption{Precision of different LLMs in citation purpose classification}
-    \label{table:evaluation}
-\end{table}
-
-\begin{figure}
-\begin{lstlisting}
-"""
-The following is a set of citation purpose categories, each category name is followed by a description of the category and an example of a sentence that belongs to this category.
-
-Name: Criticizing
-Description: Criticism can be positive or negative.
-A citing sentence is classified as "criticizing" when it mentions the weakness/strengths of the cited approach, negatively/positively criticizes the cited approach, negatively/positively evaluates the cited source.
-Example: Chiang (2005) introduced a constituent feature to reward phrases that match a syntactic tree but did not yield significant improvement.
-
-Name: Comparison
-Description: A citing sentence is classified as "comparison" when it compares or contrasts the work in the cited paper to the author's work.
-It overlaps with the first category when the citing sentence says one approach is not as good as the other approach.
-In this case we use the first category.
-Example: Our approach permits an alternative to minimum error-rate training (MERT; Och, 2003);
-
-Name: Use
-Description: A citing sentence is classified as "use" when the citing paper uses the method, idea or tool of the cited paper.
-Example: We perform the MERT training (Och, 2003) to tune the optimal feature weights on the development set.
-
-Name: Substantiating
-Description: A citing sentence is classified as "substantiating" when the results, claims of the citing work substantiate, verify the cited paper and support each other.
-Example: It was found to produce automated scores, which strongly correlate with human judgements about translation fluency (Papineni et al. , 2002).
-
-Name: Basis
-Description: A citing sentence is classified as "basis" when the author uses the cited work as starting point or motivation and extends on the cited work.
-Example: Our model is derived from the hidden-markov model for word alignment (Vogel et al., 1996; Och and Ney, 2000).
-
-Name: Neutral (Other)
-Description: A citing sentence is classified as "neutral" when it is a neutral description of the cited work or if it doesn't come under any of the above categories.
-Example: The solutions of these problems depend heavily on the quality of the word alignment (Och and Ney, 2000).
-
-Classify the following in text citation into one of these categories. Only use a single category for each citation. Respond with only a single word, the name of the category.
-
-{Citation Context}
-"""
-\end{lstlisting}
-\caption{Prompt template used for citation purpose classification}
-\label{figure:prompt-template}
-\end{figure}
+We can see that the Solar 10.7B has the highest average recall, and second highest average precision.
+We can also see that the Solar 10.7B has the most consistent scores among classes, which is important for our analysis.
+Therefore, we chose Solar 10.7B as our LLM.
 
 \section{Results}
-Initial results
 
@@
       symbolic x 
-      coords={criticizing, comparison, use, substantiating, basis, neutral},
+      coords={Positive, Neutral, Negative, Bad Context},
       scaled ticks=false,
@@
       \addplot[ybar,fill=gray] coordinates {
-          (criticizing, 560986)
-          (comparison, 12122)
-          (use,43646)
-          (substantiating, 14860)
-          (basis, 8057)
-          (neutral, 57938)
+          (Positive, 150639)
+          (Neutral, 457463)
+          (Negative, 59054)
+          (Bad Context, 30453)
       };
@@
   \end{tikzpicture}
-  \caption{Distribution of Vulnerabilities }
-  \label{graph:1}
+  \caption{Distribution of citation purposes}
+  \label{graph:distribution}
 \end{Figure}
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}{0.3\textwidth}
+    \begin{tikzpicture}
+      \begin{axis}[
+          width=(1\textwidth),
+          xlabel={Negative Citation percentage [\%]},
+          ylabel={H-index},
+          xmin=0, xmax=30,
+          ymin=0, ymax=80,
+          xtick={0, 5, 10, 15, 20, 25, 30},
+          ytick={0,10,20,30,40,50,60,70,80},
+          ymajorgrids=true,
+          grid style=dashed,
+        ]
+
+        \addplot[
+          only marks, color=blue, mark size=1.3pt
+          ]
+          coordinates {
+            (15.15,16)(10.55,16)(14.44,5)(7.21,23)(9.57,23)(7.83,22)(18.18,7)(8.52,18)(6.66,25)(3.92,11)(9.46,32)(6.8,26)(4.01,18)(11.46,66)(7.98,40)(7.73,5)(11.38,23)(12.7,14)(16.05,13)(6.53,24)(7.17,46)(5.53,39)(8.88,31)(10.06,39)(11.83,17)(5.42,16)(8.27,20)(5.59,12)(4.55,23)(10.45,40)(15.78,50)(14.08,19)(12.64,17)(7.23,22)(10.09,10)(6.36,9)(14.99,15)(14.88,33)(7.43,43)(6.77,7)(7.47,45)(8.47,26)(5.62,23)(4.71,31)(14.61,16)(14.2,36)(5.3,31)(9.81,23)(4.1,22)(7.8,16)(7.02,30)(8.63,39)(9.7,26)(11.65,14)(6.63,77)(13.58,8)(6.42,8)(3.52,22)(10.21,7)(7.27,13)(7.69,25)(17.37,14)(13.87,34)(12.28,34)(10.97,8)(5.24,23)(5.61,15)(6.22,20)(10.06,52)(6.38,45)(6.13,20)(11.54,18)(6.08,31)(6.52,18)(4.33,31)(4.03,38)(3.03,10)(7.61,5)(3.53,25)(10.42,22)(15.11,10)(8.56,30)(8.61,16)(8.67,33)(12.79,30)(7.81,13)(4.99,25)(6.04,20)(10.93,20)(11.32,2)(8.76,29)(23.61,8)(9.54,26)(19.64,6)(6.27,19)(5.71,19)
+          };
+          \addlegendentry{Researchers}
+
+        \addplot[
+          mark=square,
+          ]
+          coordinates {
+            (3.33,26.55)(6.67,24.72)(10.0,22.88)(13.33,21.05)(16.67,19.22)(20.0,17.38)(23.33,15.55)(26.67,13.71)
+          };
+          \addlegendentry{Least Squares Fit}
+
+      \end{axis}
+    \end{tikzpicture}
+    \caption{Negative citation percentage vs. H-index}
+    \label{graph:negative-karma}
+\end{subfigure}
+\hfill
+\begin{subfigure}{0.3\textwidth}
+  \begin{tikzpicture}
+    \begin{axis}[
+        width=(1\textwidth),
+        xlabel={Positive Citation percentage [\%]},
+        ylabel={H-index},
+        xmin=13, xmax=36,
+        ymin=0, ymax=80,
+        xtick={10, 15, 20, 25, 30, 35},
+        ytick={0,10,20,30,40,50,60,70,80},
+        ymajorgrids=true,
+        grid style=dashed,
+    ]
+
+    \addplot[
+      only marks, color=blue, mark size=1.3pt
+      ]
+      coordinates {
+        (14.41,16)(17.0,16)(17.78,5)(24.68,23)(19.13,23)(19.33,22)(22.76,7)(28.28,18)(19.87,25)(29.9,11)(20.85,32)(19.76,26)(26.18,18)(20.34,66)(24.02,40)(22.5,5)(22.14,23)(24.5,14)(19.89,13)(23.41,24)(22.3,46)(31.03,39)(26.83,31)(22.64,39)(19.15,17)(18.13,16)(21.89,20)(24.79,12)(23.59,23)(17.62,40)(24.89,50)(24.04,19)(29.95,17)(29.24,22)(23.93,10)(23.2,9)(20.94,15)(17.69,33)(27.17,43)(25.51,7)(18.74,45)(21.07,26)(23.45,23)(18.46,31)(21.13,16)(21.83,36)(22.45,31)(23.58,23)(30.44,22)(34.38,16)(20.07,30)(23.37,39)(20.26,26)(24.53,14)(25.63,77)(18.5,8)(24.34,8)(22.89,22)(22.49,7)(20.61,13)(19.53,25)(20.02,14)(21.83,34)(24.24,34)(18.28,8)(19.51,23)(25.63,15)(24.71,20)(16.59,52)(21.4,45)(21.36,20)(22.01,18)(20.86,31)(17.49,18)(22.07,31)(15.97,38)(25.81,10)(29.35,5)(20.88,25)(21.51,22)(22.24,10)(19.74,30)(17.63,16)(25.72,33)(21.32,30)(22.06,13)(21.52,25)(19.78,20)(22.19,20)(20.75,2)(24.05,29)(24.23,8)(24.38,26)(20.79,6)(23.72,19)(17.95,19)
+      };
+      \addlegendentry{Researchers}
+
+    \addplot[
+      mark=square,
+      ]
+      coordinates {
+        (15.0,24.7)(17.38,24.27)(19.75,23.83)(22.12,23.4)(24.5,22.96)(26.88,22.53)(29.25,22.09)(31.63,21.66)(34.0,21.22)
+      };
+      \addlegendentry{Least Squares Fit}
+
+    \end{axis}
+    \end{tikzpicture}
+    \caption{Positive citation percentage vs. H-index}
+    \label{graph:positive-karma}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.3\textwidth}
+    \begin{tikzpicture}
+      \begin{axis}[
+          width=(1\textwidth),
+          xlabel={Neutral Citation percentage [\%]},
+          ylabel={H-index},
+          xmin=49, xmax=82,
+          ymin=0, ymax=80,
+          xtick={50, 55, 60, 65, 70, 75, 80},
+          ytick={0,10,20,30,40,50,60,70,80},
+          ymajorgrids=true,
+          grid style=dashed,
+      ]
+
+      \addplot[
+        only marks, color=blue, mark size=1.3pt
+        ]
+        coordinates {
+          (70.44,16)(72.45,16)(67.78,5)(68.11,23)(71.3,23)(72.84,22)(59.06,7)(63.2,18)(73.47,25)(66.18,11)(69.69,32)(73.44,26)(69.81,18)(68.2,66)(68.0,40)(69.77,5)(66.48,23)(62.79,14)(64.06,13)(70.05,24)(70.53,46)(63.44,39)(64.29,31)(67.3,39)(69.02,17)(76.45,16)(69.85,20)(69.62,12)(71.86,23)(71.93,40)(59.32,50)(61.88,19)(57.42,17)(63.52,22)(65.97,10)(70.43,9)(64.07,15)(67.43,33)(65.4,43)(67.73,7)(73.79,45)(70.47,26)(70.92,23)(76.83,31)(64.27,16)(63.97,36)(72.25,31)(66.61,23)(65.47,22)(57.82,16)(72.92,30)(68.0,39)(70.04,26)(63.82,14)(67.74,77)(67.91,8)(69.23,8)(73.59,22)(67.3,7)(72.12,13)(72.78,25)(62.61,14)(64.3,34)(63.49,34)(70.75,8)(75.25,23)(68.77,15)(69.08,20)(73.35,52)(72.22,45)(72.52,20)(66.46,18)(73.06,31)(75.99,18)(73.59,31)(80.0,38)(71.16,10)(63.04,5)(75.59,25)(68.07,22)(62.65,10)(71.69,30)(73.76,16)(65.61,33)(65.89,30)(70.13,13)(73.49,25)(74.18,20)(66.88,20)(67.92,2)(67.19,29)(52.16,8)(66.08,26)(59.57,6)(70.01,19)(76.34,19)
+        };
+        \addlegendentry{Researchers}
+
+      \addplot[
+        mark=square,
+        ]
+        coordinates {
+          (50.0,14.63)(53.75,16.4)(57.5,18.17)(61.25,19.94)(65.0,21.71)(68.75,23.48)(72.5,25.24)(76.25,27.01)(80.0,28.78)
+        };
+        \addlegendentry{Least Squares Fit}
+
+      \end{axis}
+      \end{tikzpicture}
+      \caption{Neutral citation percentage vs. H-index}
+      \label{graph:neutral-karma}
+    \end{subfigure}
+    \caption{Citation purpose percentages vs. H-index of researchers}
+    \label{fig:researcher-karma}
+\end{figure*}
+
+\begin{figure}
+  \begin{tikzpicture}
+    \begin{axis}[
+        /pgf/number format/1000 sep={},
+        ylabel={Citation Sentiment Percentage Change [\%]},
+        xlabel={Year},
+        ymin=-10, ymax=30,
+        xmin=1999, xmax=2025,
+        ytick={-5, 0, 5, 10, 15, 20, 25}, % 40, 50, 60, 70, 80},
+        xtick={2000, 2005, 2010, 2015, 2020, 2025},
+        ymajorgrids=true,
+        grid style=dashed,
+        legend style={at={(0.5,-0.5)},anchor=south},
+        every axis plot/.append style={very thick}
+    ]
+    \addplot[
+      red
+      ]
+      coordinates {
+        (2000,0.0)(2001,-6.89)(2002,6.41)(2003,14.17)(2004,7.38)(2005,5.46)(2006,-3.63)(2007,-6.46)(2008,4.31)(2009,7.41)(2010,1.63)(2011,10.81)(2012,3.27)(2013,2.26)(2014,11.97)(2015,12.98)(2016,22.32)(2017,12.63)(2018,10.3)(2019,13.03)(2020,19.53)(2021,19.05)(2022,16.14)(2023,26.52)
+      };
+      \addlegendentry{Negative Citation}
+
+    \addplot[teal]
+      coordinates {
+        (2000,0.0)(2001,-0.77)(2002,4.82)(2003,1.13)(2004,-1.77)(2005,6.03)(2006,10.46)(2007,8.17)(2008,10.21)(2009,5.34)(2010,4.7)(2011,6.28)(2012,8.05)(2013,8.59)(2014,6.44)(2015,4.86)(2016,9.03)(2017,10.24)(2018,10.57)(2019,8.28)(2020,10.97)(2021,10.02)(2022,14.42)(2023,12.63)
+      };
+      \addlegendentry{Positive Citation}
+
+    \addplot[gray]
+      coordinates {
+        (2000,0.0)(2001,0.98)(2002,-2.11)(2003,-1.89)(2004,-0.3)(2005,-2.36)(2006,-2.65)(2007,-1.67)(2008,-3.45)(2009,-2.37)(2010,-1.55)(2011,-3.02)(2012,-2.71)(2013,-2.75)(2014,-3.2)(2015,-2.85)(2016,-5.1)(2017,-4.38)(2018,-4.22)(2019,-3.85)(2020,-5.36)(2021,-5.02)(2022,-5.99)(2023,-6.61)
+      };
+      \addlegendentry{Neutral Citation}
+
+    \end{axis}
+    \end{tikzpicture}
+    \caption{Citation sentiment percentage change throughout years}
+    \label{graph:year-karma}
+\end{figure}
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}{0.3\textwidth}
+    \begin{tikzpicture}
+      \begin{axis}[
+          width=(1\textwidth),
+          ylabel={Negative Citation percentage [\%]},
+          xlabel={Researcher's number of papers},
+          ymin=0, ymax=30,
+          xmin=0, xmax=700,
+          ytick={0, 5, 10, 15, 20, 25, 30},
+          xtick={0, 100, 200, 300, 400, 500, 600, 700},
+          ymajorgrids=true,
+          grid style=dashed,
+        ]
+
+        \addplot[
+          only marks, color=blue, mark size=1.3pt
+          ]
+          coordinates {
+            (34,15.15)(64,10.55)(7,14.44)(99,7.21)(109,9.57)(152,7.83)(27,18.18)(54,8.52)(83,6.66)(31,3.92)(211,9.46)(219,6.8)(62,4.01)(674,11.46)(129,7.98)(8,7.73)(75,11.38)(36,12.7)(55,16.05)(58,6.53)(252,7.17)(88,5.53)(226,8.88)(178,10.06)(75,11.83)(87,5.42)(38,8.27)(40,5.59)(113,4.55)(188,10.45)(155,15.78)(41,14.08)(50,12.64)(67,7.23)(30,10.09)(21,6.36)(40,14.99)(95,14.88)(179,7.43)(22,6.77)(176,7.47)(50,8.47)(106,5.62)(262,4.71)(87,14.61)(215,14.2)(169,5.3)(177,9.81)(79,4.1)(47,7.8)(117,7.02)(128,8.63)(98,9.7)(44,11.65)(493,6.63)(35,13.58)(22,6.42)(65,3.52)(19,10.21)(41,7.27)(170,7.69)(27,17.37)(107,13.87)(126,12.28)(24,10.97)(73,5.24)(29,5.61)(77,6.22)(380,10.06)(229,6.38)(58,6.13)(63,11.54)(107,6.08)(56,6.52)(152,4.33)(393,4.03)(16,3.03)(14,7.61)(70,3.53)(49,10.42)(18,15.11)(228,8.56)(46,8.61)(80,8.67)(124,12.79)(53,7.81)(205,4.99)(104,6.04)(65,10.93)(6,11.32)(109,8.76)(17,23.61)(98,9.54)(17,19.64)(42,6.27)(42,5.71)
+          };
+          \addlegendentry{Researchers}
+
+        \addplot[
+          mark=square,
+          ]
+          coordinates {
+            (0.0,9.74)(86.25,9.25)(172.5,8.76)(258.75,8.27)(345.0,7.78)(431.25,7.29)(517.5,6.8)(603.75,6.31)(690.0,5.82)
+          };
+          \addlegendentry{Least Squares Fit}
+
+      \end{axis}
+    \end{tikzpicture}
+    \caption{Negative citation percentage vs. H-index}
+    \label{graph:negative-career}
+\end{subfigure}
+\hfill
+\begin{subfigure}{0.3\textwidth}
+  \begin{tikzpicture}
+    \begin{axis}[
+        width=(1\textwidth),
+        ylabel={Positive Citation percentage [\%]},
+        xlabel={Researcher's number of papers},
+        ymin=13, ymax=36,
+        xmin=0, xmax=700,
+        ytick={15, 20, 25, 30, 35},
+        xtick={0, 100, 200, 300, 400, 500, 600, 700},
+        ymajorgrids=true,
+        grid style=dashed,
+    ]
+
+    \addplot[
+      only marks, color=blue, mark size=1.3pt
+      ]
+      coordinates {
+        (34,14.41)(64,17.0)(7,17.78)(99,24.68)(109,19.13)(152,19.33)(27,22.76)(54,28.28)(83,19.87)(31,29.9)(211,20.85)(219,19.76)(62,26.18)(674,20.34)(129,24.02)(8,22.5)(75,22.14)(36,24.5)(55,19.89)(58,23.41)(252,22.3)(88,31.03)(226,26.83)(178,22.64)(75,19.15)(87,18.13)(38,21.89)(40,24.79)(113,23.59)(188,17.62)(155,24.89)(41,24.04)(50,29.95)(67,29.24)(30,23.93)(21,23.2)(40,20.94)(95,17.69)(179,27.17)(22,25.51)(176,18.74)(50,21.07)(106,23.45)(262,18.46)(87,21.13)(215,21.83)(169,22.45)(177,23.58)(79,30.44)(47,34.38)(117,20.07)(128,23.37)(98,20.26)(44,24.53)(493,25.63)(35,18.5)(22,24.34)(65,22.89)(19,22.49)(41,20.61)(170,19.53)(27,20.02)(107,21.83)(126,24.24)(24,18.28)(73,19.51)(29,25.63)(77,24.71)(380,16.59)(229,21.4)(58,21.36)(63,22.01)(107,20.86)(56,17.49)(152,22.07)(393,15.97)(16,25.81)(14,29.35)(70,20.88)(49,21.51)(18,22.24)(228,19.74)(46,17.63)(80,25.72)(124,21.32)(53,22.06)(205,21.52)(104,19.78)(65,22.19)(6,20.75)(109,24.05)(17,24.23)(98,24.38)(17,20.79)(42,23.72)(42,17.95)
+      };
+      \addlegendentry{Researchers}
+
+    \addplot[
+      mark=square,
+      ]
+      coordinates {
+        (0.0,22.99)(86.25,22.47)(172.5,21.95)(258.75,21.43)(345.0,20.92)(431.25,20.4)(517.5,19.88)(603.75,19.36)(690.0,18.84)
+      };
+      \addlegendentry{Least Squares Fit}
+
+    \end{axis}
+    \end{tikzpicture}
+    \caption{Positive citation percentage vs. H-index}
+    \label{graph:positive-career}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.3\textwidth}
+    \begin{tikzpicture}
+      \begin{axis}[
+          width=(1\textwidth),
+          ylabel={Neutral Citation percentage [\%]},
+          xlabel={Researcher's number of papers},
+          ymin=49, ymax=82,
+          xmin=0, xmax=700,
+          ytick={50, 55, 60, 65, 70, 75, 80},
+          xtick={0, 100, 200, 300, 400, 500, 600, 700},
+          ymajorgrids=true,
+          grid style=dashed,
+      ]
+
+      \addplot[
+        only marks, color=blue, mark size=1.3pt
+        ]
+        coordinates {
+          (34,70.44)(64,72.45)(7,67.78)(99,68.11)(109,71.3)(152,72.84)(27,59.06)(54,63.2)(83,73.47)(31,66.18)(211,69.69)(219,73.44)(62,69.81)(674,68.2)(129,68.0)(8,69.77)(75,66.48)(36,62.79)(55,64.06)(58,70.05)(252,70.53)(88,63.44)(226,64.29)(178,67.3)(75,69.02)(87,76.45)(38,69.85)(40,69.62)(113,71.86)(188,71.93)(155,59.32)(41,61.88)(50,57.42)(67,63.52)(30,65.97)(21,70.43)(40,64.07)(95,67.43)(179,65.4)(22,67.73)(176,73.79)(50,70.47)(106,70.92)(262,76.83)(87,64.27)(215,63.97)(169,72.25)(177,66.61)(79,65.47)(47,57.82)(117,72.92)(128,68.0)(98,70.04)(44,63.82)(493,67.74)(35,67.91)(22,69.23)(65,73.59)(19,67.3)(41,72.12)(170,72.78)(27,62.61)(107,64.3)(126,63.49)(24,70.75)(73,75.25)(29,68.77)(77,69.08)(380,73.35)(229,72.22)(58,72.52)(63,66.46)(107,73.06)(56,75.99)(152,73.59)(393,80.0)(16,71.16)(14,63.04)(70,75.59)(49,68.07)(18,62.65)(228,71.69)(46,73.76)(80,65.61)(124,65.89)(53,70.13)(205,73.49)(104,74.18)(65,66.88)(6,67.92)(109,67.19)(17,52.16)(98,66.08)(17,59.57)(42,70.01)(42,76.34)
+        };
+        \addlegendentry{Researchers}
+
+      \addplot[
+        mark=square,
+        ]
+        coordinates {
+          (0.0,67.26)(86.25,68.27)(172.5,69.28)(258.75,70.29)(345.0,71.3)(431.25,72.31)(517.5,73.32)(603.75,74.33)(690.0,75.34)
+        };
+        \addlegendentry{Least Squares Fit}
+
+      \end{axis}
+      \end{tikzpicture}
+      \caption{Neutral citation percentage vs. H-index}
+      \label{graph:neutral-career}
+    \end{subfigure}
+    \caption{Citation purpose percentages vs. researchers' number of papers}
+    \label{fig:researcher-career}
+\end{figure*}
+
+\begin{figure}
+  \begin{tikzpicture}
+    \begin{axis}[
+        ybar=10pt,
+        bar width=15pt,
+        enlarge x limits=0.25,
+        legend style={at={(0.5,-0.15)},
+          anchor=north,legend columns=-1},
+        ylabel={Percentage of Citation Purposes [\%]},
+        symbolic x coords={Positive,Neutral,Negative},
+        xtick=data,
+        nodes near coords={\pgfmathprintnumber\pgfplotspointmeta\%},
+        nodes near coords align={vertical},
+        ]
+    \addplot coordinates {(Positive,25.1) (Neutral,67.4) (Negative,7.5)};
+    \addplot coordinates {(Positive,22.5) (Neutral,68.6) (Negative,8.9)};
+    \legend{Same Institution,Different Institution}
+    \end{axis}
+    \end{tikzpicture}
+    \caption{Citation purpose percentages within and outside of the institution}
+    \label{graph:institute-karma}
+\end{figure}
+
+We see a distribution of 21.59\% positive, 65.58\% neutral, 8.47\% negative, and 4.37\% bad context in Figure \ref{graph:distribution}.
+This data might not represent the actual distribution of citation sentiments in computer science because all the papers being cited belongs to University of Waterloo professors.
+Given that University of Waterloo has a relatively high ranking in computer science it is possible that the distribution of citation sentiments is skewed towards positive and neutral.
+
+\subsection{RQ1: Does Citation Karma Exists?}
+When we graph the citation sentiment percentages against the H-index of researchers, we see a negative correlation between negative citation percentage and H-index in Figure \ref{graph:negative-karma}.
+We also see a very slight negative correlation between positive citation percentage and H-index in Figure \ref{graph:positive-karma}.
+However, we see a positive correlation between neutral citation percentage and H-index in Figure \ref{graph:neutral-karma}.
+While it looks easy to jump into the conclusion that there is a karma effect meaning, when you give too much negative references you will get lower number of citations.
+However, this could be related to the career stage of the researcher as we will see in the next section.
+
+\subsection{RQ2: How does the citation sentiment percentages change throughout the career of a researcher?}
+We decided to use the number of papers published by a researcher as an indication of the career stage of the researcher.
+When we graph the researchers citation sentiment percentages and their number of published papers we get the graphs in Figure \ref{fig:researcher-career}, we can see that as the researchers publish more papers the negative and positive citation percentages decrease and neutral citation percentages increase.
+We can hypothesize that as the researchers get more experienced they tend to give more neutral references.
+This can also explain the negative correlation between the negative and positive citation percentage and H-index and positive correlation between neutral citation percentage and H-index.
+This is because H-index is also an indirect measure of the career stage of a researcher, as more experienced researchers tend to have higher H-indexes.
+
+\subsection{RQ3: How did the distribution of citation sentiments changed over time?}
+We calculated the average citation sentiment percentages for each year from 2000 to 2023, these citations include both the citations the Waterloo professors received and the citations they gave.
+We then graphed the percentage changes of the three classes in Figure \ref{graph:year-karma}.
+As you can see there is a consistent increase in positive and negative citation percentages and a consistent decrease in neutral citation percentage.
+This could potentially mean that the computer science community is getting more polarized over time.
+
+\subsection{RQ4: Does being in the same institution affect the citation sentiment distribution?} 
+We calculated the average citation sentiment percentages for citations given to University of Waterloo professors by other University of Waterloo professors and by professors from other institutions.
+We then graphed the results in Figure \ref{graph:institute-karma}.
+We can see that the distribution of citation sentiments is very similar for both cases.
+However, we can see a 2.6\% increase in positive citation percentage and a 1.4\% decrease in negative citation percentage when the citation is given by a professor from the same institution.
+This could potentially point to a slight positive bias towards professors from the same institution.
+
+\section{Conclusion}
+In conclusion, our analysis of citation sentiments among University of Waterloo professors in computer science reveals intriguing patterns.
+While the overall distribution suggests a predominantly positive and neutral sentiment, it's essential to acknowledge the potential skew introduced by the university's high ranking.
+Examining the existence of "Citation Karma," we observed a nuanced relationship between citation sentiments and researchers' H-index, hinting at a possible correlation with career stage.
+
+Exploring the evolution of sentiments throughout researchers' careers, we found a tendency for more experienced researchers to provide increasingly neutral references, aligning with the observed correlations.
+The temporal analysis indicates a growing polarization in the computer science community, reflected in rising positive and negative citation percentages alongside a decline in neutral citations over time.
+
+Furthermore, our investigation into the influence of institutional affiliation on citation sentiment distribution suggests a subtle positive bias when citations originate from the same institution.
+These findings contribute to a deeper understanding of the dynamics shaping scholarly communication within a specific academic community.
+
+In summary, our study sheds light on the complex interplay of factors influencing citation sentiments, ranging from individual career stages to institutional affiliations and temporal shifts.
+These insights encourage further exploration into the evolving landscape of scholarly interactions and their implications for the dynamics of academic discourse.
 
@@
 %% If your work has an appendix, this is the place to put it.
+\appendix
+
+\section{Classification Prompt Template}
+\label{appendix:classification-prompt}
+The following is a set of citation sentiment categories, each category name is followed by a description of the category and some examples of in-text citation contexts that belongs to this category.
+
+\begin{itemize}
+  \item \textbf{Name}: Positive
+
+  \textbf{Description}: A citing sentence is classified as "positive" when it mentions the strength of the cited approach, positively criticizes the cited approach, positively evaluates the cited source, uses the cited source as a starting point or motivation and extends on the cited work, or when the results, claims of the citing work substantiate, verify the cited paper and support each other.
+
+  \textbf{Example 1}: Researchers [13] have presented a Secure and Efficient Topology Discovery Protocol (sOFTDP) that shifts a part of the link discovery to the SDN switch.
+
+  \textbf{Example 2}: To obtain more precise and descriptive topics, we further conducted GuidedLDA [24] using some of the most salient keywords selected from our initial LDA results.
+
+  \item \textbf{Name}: Negative
+
+  \textbf{Description}: A citing sentence is classified as "negative" when it mentions the weakness of the cited approach, negatively criticizes the cited approach, negatively evaluates the cited source.
+
+  \textbf{Example 1}: Most of the existing literature on the execution cost problem focus on markets where only one investor trades (for instance see [3, 4, 5, 6, 8, 9]).
+
+  \textbf{Example 2}: With nonlinear CI test, LPCMCI is computationally too expensive to be compared when the number of nodes is large.
+
+  \item \textbf{Name}: Neutral
+
+  \textbf{Description}: A citing sentence is classified as "neutral" when it is a neutral description of the cited work. Use this category when there is no strong criticism negatively or positively.
+
+  \textbf{Example 1}: Since the inception of spam, many companies and research teams have combined their efforts to fight against spam deliveries using different approaches and methods [1].
+
+  \textbf{Example 2}: Conventional approaches adopt fine-tuned generative models (Zhong et al., 2020b; Guo et al., 2021; Wang et al., 2021a, inter alia ) as input generators, with a semantic parser (e.g., PCFG grammar) for sampling symbolic outputs.
+
+  \item \textbf{Name}: Bad Context
+
+  \textbf{Description}: A citing sentence is classified as "bad context" when the given context is not enough to classify the citation or it does not include any citation.
+
+  \textbf{Example 1}: But then, the sum of welfare lost + retained is the optimum welfare and is bounded.
+
+  \textbf{Example 2}: Furthermore, since step (4) did not return FAIL, we must have g; a divisor of all entries in V' and W' hence JV contains only polynomial entries.  
+\end{itemize}
+
+Classify the following in text citation into one of these categories. First, type 'THINKING:' and write your reasoining step by step. Then type 'ANSWER:' and give your answer in a single word.
+
+\{Citation Context\}
 

### 2023-12-30 citeq/evaluate.py

@@ -25,11 +25,11 @@ with open("citations_annotated.csv", "r") as f:
 llm_annotations = []
 for citation in tqdm(annotated_citations):
     citation_context = session.query(Citation).filter(Citation.id == citation[0]).first().context
-    predicted_class = LlmClassifier.get_sentiment_class(citation_context, "mistral")
+    predicted_class = LlmClassifier.get_sentiment_class(citation_context, "llama")
     llm_annotations.append([citation[0], int(citation[1] if citation[1] != 3 else "2"), predicted_class.value])
 
 # write the llm annotations to a file
-with open("llm_annotations_mistral_inst.csv", "w") as f:
+with open("llm_annotations_llama.csv", "w") as f:
     for annotation in llm_annotations:
         f.write(f"{annotation[0]},{annotation[1]},{annotation[2]}\n")
 

### 2023-12-30 citeq/insert_llm_out.py

@@ -6,19 +6,18 @@ from tqdm import tqdm
 
 
 class SentimentClass(Enum):
-    CRITICIZING = 0
-    COMPARISON = 1
-    USE = 2
-    SUBSTANTIATING = 3
-    BASIS = 4
-    NEUTRAL_OR_UNKNOWN = 5
+    POSITIVE = 0
+    NEGATIVE = 1
+    NEUTRAL = 2
+    BAD_CONTEXT = 3
 
 
 # Create a session to use the tables
 session = Session(engine)
-
+path = "llm_purpose_649000_697609.csv"
+print(f"Reading {path}...")
 # Update the citation purposes with the llm output
-with open("llm_purpose_5.csv", "r") as f:
+with open(path, "r") as f:
     citations = f.readlines()
     for citation in tqdm(citations):
         c_id, annotation = citation.split(",")

### 2023-12-30 citeq/llm_classifier.py

@@ -171,9 +171,10 @@ class SentimentClass(Enum):
 
 class LlmClassifier:
     llm_mistral = Ollama(model="mistral")
-    llm_gpt = normalize_gpt(ChatOpenAI(model="gpt-3.5-turbo-1106"))
-    llm_gpt4 = normalize_gpt(ChatOpenAI(model="gpt-4"))
-    LLM = {"mistral": llm_mistral, "gpt3": llm_gpt, "gpt4": llm_gpt4}
+    llm_llama = Ollama(model="llama2")
+    llm_gpt = None  # normalize_gpt(ChatOpenAI(model="gpt-3.5-turbo-1106"))
+    llm_gpt4 = None  # normalize_gpt(ChatOpenAI(model="gpt-4"))
+    LLM = {"mistral": llm_mistral, "gpt3": llm_gpt, "gpt4": llm_gpt4, "llama": llm_llama}
     promt_printed = False
 
     @staticmethod

### 2024-04-03 paper/main.tex
up

@@
 %% complete the rights form.
-\setcopyright{acmlicensed}
-\copyrightyear{2018}
-\acmYear{2018}
-\acmDOI{XXXXXXX.XXXXXXX}
+
+% \setcopyright{acmlicensed}
+% \copyrightyear{2018}
+% \acmYear{2018}
+% \acmDOI{XXXXXXX.XXXXXXX}
 
 %% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Conference acronym 'XX]{Make sure to enter the correct
-  conference title from your rights confirmation emai}{June 03--05,
-  2018}{Woodstock, NY}
+
+% \acmConference[Conference acronym 'XX]{Make sure to enter the correct
+%   conference title from your rights confirmation emai}{June 03--05,
+%   2018}{Woodstock, NY}
+
   %%
@@
 %%  June 03--05, 2018, Woodstock, NY}
-\acmISBN{978-1-4503-XXXX-X/18/06}
+
+% \acmISBN{978-1-4503-XXXX-X/18/06}
 
@@
 \email{oearpaci@uwaterloo.ca}
+\affiliation{%
+  \institution{University of Waterloo}
+  \streetaddress{200 University Ave W}
+  \city{Waterloo}
+  \state{Ontario}
+  \country{Canada}
+  \postcode{N2L 3G1}
+}
+
+\author{Yahya Jabary}
+\email{yahya.jabary@uwaterloo.ca}
 \affiliation{%
@@
 
-\received{20 February 2007}
-\received[revised]{12 March 2009}
-\received[accepted]{5 June 2009}
+% \received{20 February ???}
+% \received[revised]{12 March ???}
+% \received[accepted]{5 June ???}
 
@@
 We formed an SQLite database, with the scheme shown in Figure \ref{fig:citeq-scheme}, to facilitate flexible querying of the data.
-This database is publicly available at \url{https://github.com/onurerenarpaci/citeQ.git}.
+This database is publicly available at \url{https://github.com/sueszli/citeQ.git}.
 
